Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-21 robdml.tex
tex

During the training process, the strength of adversary will gradually decrease,
because the expectation of the destination hardness $E[H_\mathsf{D}]$ is expected to
decrease with a model being trained.

strong example when the embedding space is not in good shape.

\begin{equation}
	%
	g_\mathsf{SGA}() = -\gamma \cdot \bar{\ell}_{t-1}
	%
\end{equation}

>>>>

% motivation of GA: early phase

However, while the destination hardness is boosted in the late phase of
training, the adversarial examples may still hamper the learning of a good
embedding space in the early phase.
%
At this point, we argue that learning from a strong adversary in the early
training phase (\ie, when the embedding space is not ``in-good-shape'') hampers the
generalization on benign examples.
%
In other words, the desired destination hardness should be (1) relatively weak
in the early training phase, and (2) relatively strong in the late training
phase.
%
We name the family of pseudo-hardness functions that fulfills the two
conditions as ``Graduate Adversary''.
%
Additionally, if we have a strong prior knowledge on ``how hard the destination
hardness should be'', the pseudo-hardness function can be independent from
any benign triplet.

% simple graduate adversary

For instance, if we assume that the destination hardness should remain
in the hardness range of Semihard~\cite{facenet}, the following function
satisfies the two condictions of Gradual Adversary, dubbed
``Simple Gradual Adversary'' (SGA):
%
\begin{equation}
	%
	g_\mathsf{SGA}() = -\gamma \cdot \bar{\ell}_{t-1} ~ \in [-\gamma,0].
	%
\end{equation}
%
The design of this function will be empirically supported in the experiments
section.
%
The exploration of other possible pseudo-hardness functions is omitted to 
keep simplicity.
